\hspace{1cm} Do syntactic and semantic similarity lead to interference effects?\newline Evidence from self-paced reading and event-related potentials using German

### 2023-10-08 paper/main.tex
changed title

\title{\hspace{1cm}Semantic interference during encoding and retrieval \newline
%Semantic (but no syntactic) similarity-based interference
Evidence from self-paced reading and event-related potentials}
\authorsnames{Pia Schoknecht, Shravan Vasishth}

\shorttitle{Semantic interference}
\affiliation{
Department of Linguistics, University of Potsdam}

>>>>

\title{\hspace{1cm} Do syntactic and semantic similarity lead to interference effects?\newline
%Semantic (but no syntactic) similarity-based interference
Evidence from self-paced reading and event-related potentials using German}
\authorsnames{Pia Schoknecht, Shravan Vasishth}

\shorttitle{Syntactic and semantic interference effects}
\affiliation{
Department of Linguistics, University of Potsdam}
